---
title: "geom_grob()"
output: rmarkdown::html_vignette
vignette:  >
  %\VignetteIndexEntry{hypoimg intro}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
---

```{css, echo=FALSE}
img {
  border: 0;
}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library("hypoimg")
```

The **hypoimg** package implements a new geom: `geom_hypo_grob()`.

This geom provides a possibility to distribute grobs over different facets of a ggplot.
It needs a tibble that organizes the grobs according to the facetting levels.

This geom builds heavily on the answer by baptiste on the tidiverse github forum [issue 1399](https://github.com/tidyverse/ggplot2/issues/1399).
To the original answer, only the parameters height, width and angle have been added.

```{r geomGrob, out.width = "100%", fig.width = 11, fig.height = 6, warning = FALSE}
# Our color map
clr <- c(RColorBrewer::brewer.pal(5,'Oranges')[3],
         RColorBrewer::brewer.pal(5,'Blues')[5])

# creating a list of grobs from single hamlet legend elements
grobs <- list(hypo_anno_single(species = 'indigo',
                               circle_fill = clr[2],
                               circle_lwd = 1,circle_color = 'black') %>%
                ggplotGrob(),
              hypo_anno_single(species = 'chlorurus',
                               circle_fill = clr[1],
                               circle_lwd = 1,circle_color = 'black') %>%
                ggplotGrob())

# The tibbble that combines grobs, aesthetic and facetting levels
grob_list <- tibble(RUN = c('ind', 'chl'),
                    angle = c(30, -30),
                    height = c(.9,.7),
                    grob = grobs)

# some fake data set
test_df <- tibble(x = rep(1:10, 2),
                  y = rnorm(20),
                  RUN = rep(c('ind', 'chl'), each = 10))

# Using geom_hypo_grob() to distribute the grobs
ggplot()+
  facet_grid(RUN~.)+
  geom_hypo_grob(data=grob_list,
                 aes(grob=grob,angle=angle,height=height),
                 inherit.aes = FALSE, x = .85, y=0.5)+
  geom_line(data = test_df,
            aes(x=x,y=y,color=RUN),size=2)+
  geom_point(data = test_df,
             aes(x=x,y=y,fill=RUN),shape=21,size=4)+
  scale_x_continuous(expand=c(0,0),limits = c(0,14))+
  scale_fill_manual(values = clr)+
  scale_color_manual(values = clr)+
  theme(legend.position = 'bottom')
```

---------------------------------

  <center>
  <img src = "logo.svg" width = 20% />
  </center>
