---
title: "The hypoimg package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hypoimg intro}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
---

```{css, echo=FALSE}
img {
  border: 0;
}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library("hypoimg")
```

## About the package:

The **hypoimg** package provides illustrations to annotate plots within studies of the Caribbean hamlets (*Hypoplectrus spp*).

It contains the basic illustrations of different hamlet species and countries where hamlets occur. Additionally, the package provides a set of functions to construct legends which link a color map with a set of hamlet species, pairwise species comparisons (or countries).

Additionally to this package, resources for the analysis of genomic data of hamlets are provided within the [**hypogen**](www.github.com/k-hench/hypogen) package.

## Installation

Using the **devtools** package, **hypoinmg** can be installed directly from github:

```{r install, eval = FALSE}
devtools::install_github("k-hench/hypoimg")
```

## Hamlet annotations

The core of the **hypoimg** package is the selection of hamlet illustrations:

```{r hypoGallery, echo = FALSE, out.width = "95%", fig.width = 12}
ggplot(tibble(x = c(0,5.2), y = c(0,0)),aes(x = x, y = y))+
  geom_blank()+theme_void()+
  coord_fixed()+
  hypo_anno_r('puella', xmin = 0, xmax = 1)+
  hypo_anno_l('providencianus', xmin = 1.2, xmax = 2.2)+
  hypo_anno_l('indigo', xmin = 2.2, xmax = 3.2)+
  hypo_anno_l('gummigutta', xmin = 3.2, xmax = 4.2)+
  hypo_anno_l('unicolor', xmin = 4.2, xmax = 5.2)+
  scale_y_continuous(limits = c(-.2,.2))+
  theme(panel.background = element_rect())
```

The package contains one left and one right facing illustration for 19 different hamlet species and morphotypes. They are made available as *grid objects* (grob) in the tibble `hypo_img`:

```{r hypoTibble}
hypo_img

```

A pure version of the hamlet annotations can be added to any ggplot using the the functions `hypo_anno_l()` and `hypo_anno_r()`. These functions are simple wrappers around the **ggplot2** function `annotation_custom(()`.

```{r pureAnno, out.width = "95%", out.height = "90%", fig.width = 9}
ggplot(tibble(x = c(3, 3.25, 3.75),y = c(-.1, -.3, .3)),
       aes(x = x, y = y))+
  geom_line(size = 4, color = "#35B779")+
  hypo_anno_r('puella', xmin = 0, xmax = 1)+
  hypo_anno_l('indigo', xmin = 1.5, xmax = 2.5)+
  coord_fixed()+
  scale_x_continuous(limits = c(0, 3.75))+
  scale_y_continuous(limits = c(-.35, .35))
```

A common task is a contrast different hamlet species in genomic or ecologic terms.
Here it might be useful to assign individual colors to the individual hamlet species.
The **hypoimg** package provides a way to create a custom legend for such a situation.

An individual color - species assignment can be shown using the `hypo_anno_single()` function:

```{r singleHypoBlock, out.width = "95%", fig.width = 12}
hypo_anno_single(species = 'aberrans',
                 circle_fill = "#35B779", circle_color = 'black',
                 plot_names = TRUE, plot_name_size = 5)
```

The same is possible for pairs of species using `hypo_anno_pair()`:

```{r pairHypoBlock, out.width = "95%", fig.width = 12}
hypo_anno_pair(left = 'ecosur', right = 'maya',
               circle_fill = "#F16913", circle_color = 'black',
               plot_names = TRUE, plot_name_size = 5)
```

If several different species are used within one plot a custom legend can be generated based on the species list and the color map using `hypo_legend_single()`.

To be able to use this legend the it needs to be transformed into a grob using `ggplot2::ggplotGrob()`.

```{r singleHypoLegend, out.width = "85%", fig.width = 8,fig.height = 8}
set.seed(5)

# For this demonstration we'll create a fake length - weight reltionship data table.
# To do this, we'll implement the relationship as stated by fishbase for H. puella:
# http://www.fishbase.se/summary/Hypoplectrus-puella.html
hamlet_length_weight <- function(x, a = 0.009, b = 3.04 , rand = 0){
  a * x^b + rnorm(length(x)) * rand
}

# The species involved in the fake data set
hamlet_species <- c('nigricans', 'unicolor', 'gemma')

# The fake dataset
hamlet_data <- tibble(species = rep(hamlet_species, each = 10),
                      len = sample(5:17, replace = TRUE , size = 30)+rnorm(30)) %>%
  mutate(weig = ifelse(species == 'nigricans',
                       hamlet_length_weight(x = len, rand = 1) + rnorm(10),
                       ifelse(species == 'unicolor',
                              hamlet_length_weight(x = len, b = 3.14,rand = 1.5),
                              hamlet_length_weight(x = len, b = 2.94,rand = 1.5))))

# Our color map
clr_single <- viridis::viridis(3)

# The custom legend is created based on the species list and the color map
legend_grob_single <- hypo_legend_single(species = hamlet_species, color_map = clr_single,
                 circle_color = 'black', plot_names = TRUE) %>%
  ggplotGrob()

# We add the custom legend using ggplot2::annotation_custom()
ggplot(hamlet_data, aes(x = len, y = weig,
                        color = species, fill = species)) +
  geom_line(size = 1.2)+
  geom_point(color = "black", size = 2.5, shape = 21)+
  annotation_custom(legend_grob_single,xmin = 3,xmax = 9.5, ymin = 42)+
  labs(x = "Length (cm)",
       y = "Weight (g)")+
  scale_color_manual(values = clr_single, guide = FALSE)+
  scale_fill_manual(values = clr_single, guide = FALSE)
```

Similarly, the pair wise elements can be combined into a legend using `hypo_legend_pair()`

```{r pairedHypoLegend, out.width = "95%", fig.width = 10,fig.height = 6}
# The species involved in the fake data set
left <- c("aberrans", "aberrans", "chlorurus")
right <- c("aberrans", "chlorurus",  "chlorurus")

# For this demonstration we'll create a fake pairing experiment with egg counts.
# this function samples counts for 15 pairings
egg_c <- function(x){sample(x,size = 15,replace = TRUE)}

# The fake dataset
pairing_data <- tibble(pair = rep(str_c(left, right, sep = "-"),
                                 each = 15),
                      pairing_egg_counts = c(egg_c(90:110),egg_c(50:95), egg_c(60:100)),
                      time_point = factor(rep(rep(c('morning','noon','evening'),
                                                 each=5),
                                             3),
                                         levels = c('morning','noon','evening')))

# Our color map
clr_pair <- RColorBrewer::brewer.pal(3,"RdBu")

# The custom legend is created based on two species lists and the color map
legend_grob_pair <- hypo_legend_pair(left = left, right = right,
                                     color_map = clr_pair,
                                     circle_color = 'black',
                                     plot_names = TRUE,
                                     circle_lwd = .5) %>%
  ggplotGrob()

# We add the custom legend using ggplot2::annotation_custom()
ggplot(pairing_data, aes(y = pairing_egg_counts,
                         x = time_point,
                         fill = pair))+
  geom_boxplot()+
  annotation_custom(legend_grob_pair,
                    xmin = 3.25, ymin = 70)+
  coord_cartesian(xlim = c(0.75,4.6))+
  labs(x = "Time point",
       y = "Egg count / pairing (n)")+
  scale_fill_manual(values = clr_pair,guide = FALSE)

```


## Flag annotations

```{r flagGallery, echo = FALSE, out.width = "95%", fig.width = 12}
ggplot(tibble(x = c(0,5.2), y = c(0,0)),aes(x = x, y = y))+
  geom_blank()+
  theme_void()+
  coord_fixed()+
  hypo_anno_flag('cuba', xmin = 0, xmax = 1)+
  hypo_anno_flag('caribbean', xmin = 2, xmax = 3)+
  hypo_anno_flag('panama', xmin = 4, xmax = 5)+
  scale_y_continuous(limits = c(-.2,.2))+
  theme(panel.background = element_rect())
```

Besides the hamlet illustrations, the **hypoimg** also provides labels for all countries of the Caribbean and the Golf of Mexico:

```{r flaggTibble}
hypo_flag
```

An overview of all the flags can be generated with `hypo_flag_palette()`.
```{r flagPalette, out.width = "100%", fig.width = 11, fig.height = 12}
hypo_flag_palette()
```

Apart from this there exist one flag version for all of the previously discussed functions:

- `hypo_anno_flag()`
- `hypo_anno_flag_single()`
- `hypo_anno_flag_pair()`
- `hypo_legend_flag_single()`
- `hypo_legend_flag_pair()`


```{r flagShowRoom, echo = FALSE, out.width = "100%", fig.width = 11, fig.height = 4}
set.seed(3)
p1 <- ggplot(data = tibble(x=seq(0,10,length.out = 50),y=sin(x)+.3*rnorm(50)),aes(x=x,y=y))+
  geom_area(fill = alpha('black',.2))+
  geom_point()+
  hypo_anno_flag('panama',xmin = 4.2,xmax = 5.2,ymin = -.5,ymax = -.05)+
  scale_x_continuous(limits = c(0,10))+coord_fixed(ratio = 3)

p2 <- hypo_anno_flag_single(geo = 'trinidad_and_tobago',
                      flag_lwd = 1, flag_line_color = 'black',
                      flag_radius_scale = 1, circle_fill = RColorBrewer::brewer.pal(3,'Blues')[3],
                      circle_color = 'black',circle_lwd = 1,plot_names = TRUE)


p3 <- hypo_legend_flag_pair(left = c('panama','mexico','cuba'),
                      right = c('mexico','cuba','panama'),
                      color_map = RColorBrewer::brewer.pal(3,'PRGn'),
                 flag_lwd = 1, flag_line_color = 'black',
                 flag_radius_scale = 1,
                 circle_color = 'black', plot_names = TRUE)

cowplot::plot_grid(p1, p2, p3, nrow = 1)
```

---------------------------------

<center>
```{r, echo = FALSE,fig.asp = 1, out.height = "150pt", out.width = "150pt"}
hypoimg:::hypo_logo()
```
</center>
